### 2025-02-20 paper/sections/appendix.qmd
noice
phew

@@

>>>>

{{< include /paper/sections/other/counterfactuals.qmd >}}

@@

# Compute {.appendix}

<!-- [@DHPC2022] -->

We performed our experiments on a high-performance cluster. Details about the cluster will be disclosed upon publication to avoid revealing information that might interfere with the double-blind review process. Since our experiments have largely involved highly parallel tasks and small models, we have made extensive use of multi-processing.

### 2025-02-20 paper/sections/other/constraints.qmd
phew

using CTExperiments: 
    get_ce_data, 
    train_val_split, 
    build_model, 
    LinearModel, 
    get_input_encoder

@@

    # Data and decision boundary:
    coeff = get_log_reg_params(model)
    db = get_decision_boundary(coeff)
    plt = Plots.scatter(
        ce_data, 
        # label=["1=Default" "2=No Default"], 
        # legend_position=:topright, 
        xlab=xlab, ylab=ylab,  
        axis=nothing, 
        legend=false,
        title=_title
    )
    Plots.abline!(plt, db.slope, db.intercept; lw=5, label="Dec. Boundary")

@@

# Data:
specs = [
    ("(a)", VanillaObjective(needs_ce=true), ["both", "both"]),
    ("(b)", FullObjective(lambda=[1.0,1.0,0.0,1.0]), ["both", "both"]),
    ("(c)", VanillaObjective(needs_ce=true), ["both", "none"]),
    ("(d)", FullObjective(lambda=[1.0,1.0,0.0,1.0]), ["both", "none"]),
]
```

@@

    # Data:
    data = LinearlySeparable(
        n_train=500,
        batchsize=50,
        mutability=constraint
    )
    global ce_data = get_ce_data(data)
    val_size = data.n_validation / (data.n_validation + data.n_train)
    train_set, val_set, _ = train_val_split(data, ce_data, val_size)

    # Model:
    nin = size(first(train_set)[1], 1)
    nout = size(first(train_set)[2], 1)
    model = build_model(LinearModel(), nin, nout)

    # Objective:
    generator = GenericGenerator()
    opt_state = Flux.setup(Descent(), model)
    conv = DecisionThresholdConvergence(decision_threshold=0.99)

    model, logs = counterfactual_training(
        obj,
        model,
        generator,
        train_set,
        opt_state;
        val_set = val_set,
        nepochs = 100,
        mutability = Symbol.(constraint),
        callback = plot_db,
        nce=50,
        convergence=conv, 
        verbose=3
    )

>>>>

using CTExperiments: 
    get_ce_data, 
    train_val_split, 
    build_model, 
    LinearModel, 
    MLPModel,
    get_input_encoder

@@

    # Data and decision boundary:
    plt = Plots.scatter(
        ce_data, 
        # label=["1=Default" "2=No Default"], 
        # legend_position=:topright, 
        xlab=xlab, ylab=ylab,  
        axis=nothing, 
        legend=false,
        title=_title
    )
    if length(model) == 1
        coeff = get_log_reg_params(model)
        db = get_decision_boundary(coeff)
        Plots.abline!(plt, db.slope, db.intercept; lw=5, label="Dec. Boundary")
    end

@@

# Data:
specs = [
    # ("(a)", VanillaObjective(needs_ce=true), ["both", "both"]),
    ("(b)", FullObjective(lambda=[1.0,0.5,0.01,1.0]), ["both", "both"]),
    # ("(c)", VanillaObjective(needs_ce=true), ["both", "none"]),
    # ("(d)", FullObjective(lambda=[1.0,1.0,0.0,1.0]), ["both", "none"]),
]
```

@@

    # Data:
    data = LinearlySeparable(
        n_train=5000,
        batchsize=50,
        mutability=constraint
    )
    global ce_data = get_ce_data(data)
    val_size = data.n_validation / (data.n_validation + data.n_train)
    train_set, val_set, _ = train_val_split(data, ce_data, val_size)

    # Model:
    nin = size(first(train_set)[1], 1)
    nout = size(first(train_set)[2], 1)
    model = build_model(MLPModel(), nin, nout)

    # Objective:
    generator = ECCoGenerator()
    opt_state = Flux.setup(Descent(), model)
    conv = DecisionThresholdConvergence(decision_threshold=0.95, max_iter=25)

    model, logs = counterfactual_training(
        obj,
        model,
        generator,
        train_set,
        opt_state;
        val_set = val_set,
        nepochs = 50,
        mutability = Symbol.(constraint),
        callback = plot_db,
        nce=1000,
        convergence=conv, 
        verbose=3
    )
